\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-11-12 doc/USER_MANUAL/01_introduction.tex
fixed two typos

>>>>

\red{In fluids, when gravity is turned off, SPECFEM3D uses the classical
linearized Euler equation; thus if you have sharp local variations of
density in the fluid (highly heterogeneous fluids
in terms of density) or if density becomes extremely small in some
regions of your model (e.g. for upper-atmosphere studies), before using
the code please make sure the linearized Euler equation is a valid
approximation in the case you want to study, and/or see if you should turn gravity on.
For more details on that see e.g. \cite{COA2011}.}\\
